COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-12-16 main.tex
Add intro to section 4.1

@@

Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear. This is due to the 
fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo 
collisions at a wide range of heliocentric distances. In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 
MMR. This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower. The random orientations of 
the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to 
the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}. Additionally, there is a 
double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation. The radial distance of these two prongs 
corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with 
Jupiter undergoes. (Need more explanation of why this happens)

>>>>

\subsection{Collision Rates}\label{sec:coll_rates}

The Safronov collision rate given by equation \ref{eq:safronov} can be a viable way to predict the collision rates of planetesimals 
using only their positions and velocities \citep{2017ApJ...850..103B}, but suffers from some limitations. First, the Safronov collision 
rate is constructed from the assumption that the planetesimal disk is azimuthally symmetric. This is not the case for the EJ 
simulation, in which the disk between resonances exhibits a well defined pericenter orientation. Although the strong precession 
induced by the MMRs does randomize the orientations of orbits near the resonances, the phase space distribution of bodies at the 
edges of the resonances becomes extremely complex and is best studied using a full N-body treatment. Secondly, as we will show 
below, the velocity distribution of planetesimals takes on a bimodal distribution near the MMRs. This makes the rms velocity of 
planetesimals not well-defined and therefore predicting the collision rate using a statistical approach becomes difficult.

@@

%Explanation of offset of feature near 3:1 in EJ: orbital orientations randomized near MMR, most bodies have ecc of e_forced, even in resonance. Geometrically, less overlap at apo, so surface density drops and so does coll rate.
Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear. This is due to the 
fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo 
collisions at a wide range of heliocentric distances. In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 
MMR. This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower. The random orientations of 
the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to 
the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}. Additionally, there is a 
double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation. The radial distance of these two prongs 
corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with 
Jupiter undergoes. (Need more explanation of why this happens)
